\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.6in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{array}
\usepackage{parskip}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=1.2em, itemsep=0.2em, topsep=0.3em}

\definecolor{resumeblue}{HTML}{0F3B5C}
\definecolor{resumegrey}{HTML}{4A5560}

\titleformat{\section}{\large\bfseries\color{resumeblue}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{0.7em}{0.45em}

\newcommand{\resumeheader}[1]{
  {\fontsize{22}{24}\selectfont\bfseries\color{resumeblue} #1}
}

\newcommand{\entry}[4]{
  \textbf{#1} \hfill \textbf{#2} \\
  {\color{resumegrey} #3} \hfill {\color{resumegrey} #4} \\
}

\begin{document}

\resumeheader{Achraf Ouazzani Chahidi}

{\color{resumeblue}\textbf{AI Security | Offensive Security | Application Security}} \\
\href{mailto:21@achux21.com}{21@achux21.com} \,|\, +86 135 9131 8052 \,|\, Dalian, China \\
\href{https://achux21.com}{achux21.com} \,|\, \href{https://github.com/ACHUX21}{github.com/ACHUX21} \,|\, \href{https://www.linkedin.com/in/achux21}{linkedin.com/in/achux21}

\section*{Summary}
AI security and application security student with hands-on experience in web exploitation, vulnerability research, and security tooling. Active CTF competitor with multiple first-place finishes and challenge-authoring experience. Building security tools that combine static analysis, offensive-security thinking, and AI-assisted detection, grounded in strong Python, C, and systems-level programming foundations.

\section*{Experience}
\entry{Junior Penetration Tester}{Jan 2025 -- Mar 2025}{Swift IT}{Casablanca, Morocco}
\begin{itemize}
  \item Performed authorized web and systems assessments focused on validating exploitable behavior and producing clear technical reporting.
  \item Validated issues including SQL injection, XSS, and IDOR during real assessments.
  \item Built a Python tool to automate detection of HTTP request smuggling behavior during engagements.
  \item Delivered proof-of-concepts, impact analysis, and remediation guidance.
\end{itemize}

\section*{Projects}
\textbf{PackGuard} \hfill {\color{resumegrey} AI Security} \\
AI-powered package security scanner for npm and PyPI focused on malicious-package detection, typosquatting patterns, and supply-chain risk review using static analysis, heuristic detection, and local AI models.

\vspace{0.4em}
\textbf{HTTP Request Smuggling Detector} \hfill {\color{resumegrey} Application Security} \\
Python tool that automates crafted-request testing for HTTP desynchronization behavior and reduces manual overhead during web assessments.

\vspace{0.4em}
\textbf{Vulnerability Scanner Suite} \hfill {\color{resumegrey} Security Automation} \\
Collection of Python and Bash utilities for reconnaissance, endpoint discovery, and lightweight fuzzing that improves speed and repeatability in web testing workflows.

\vspace{0.4em}
\textbf{Custom Shell in C} \hfill {\color{resumegrey} Systems Programming} \\
Unix-like shell built in C to understand parsing, process management, execution flow, and low-level debugging.

\section*{Security Research \& Community}
\begin{itemize}
  \item Published 10+ writeups covering SSRF, SSTI, SQLi, JWT, and RCE at \href{https://blog.achux21.com}{blog.achux21.com}.
  \item Active CTF competitor with AKASEC and multiple top placements across 2024 and 2025 events.
  \item Designed and authored web exploitation challenges for multiple CTF competitions.
\end{itemize}

\section*{Achievements \& Certifications}
\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}X>{\raggedleft\arraybackslash}p{1.9in}@{}}
eJPTv2, INE & Certified \\
Cisco Networking Academy Coursework & Completed \\
MCSCv12 CTF 2025 -- 1st Place & 2025 \\
IDEHv6 CTF 2025 -- 1st Place & 2025 \\
AISEC CTF 2025 -- 1st Place & 2025 \\
Cyber Odyssey CTF 2024 -- 2nd Place & 2024 \\
HTB Cyber Apocalypse 2024 -- Top 15 (Team L3ak) & 2024 \\
\end{tabularx}

\section*{Education}
\entry{B.Sc. in Computer Science (in progress)}{2025 -- 2029}{Dalian Polytechnic University}{Dalian, China}
\entry{Technician Degree in Cybersecurity}{2023 -- 2025}{Specialized Institute of Management and Computer Science}{Casablanca, Morocco}

\section*{Skills}
\textbf{Programming:} Python, C, Bash, JavaScript \\
\textbf{Security:} Web Exploitation, SQLi, XSS, SSRF, IDOR, Application Security, OWASP \\
\textbf{AI Security:} Supply Chain Security, Static Analysis, AI-Assisted Detection \\
\textbf{Tools:} Burp Suite, Nmap, ffuf, sqlmap, Metasploit, Docker, Linux \\
\textbf{Research:} CTF Writeups, Challenge Authoring, Vulnerability Research, Technical Reporting

\section*{Languages}
Arabic (Native), English (Fluent), French (Fluent), Mandarin Chinese (Basic, HSK 1)

\end{document}
